Lobbying and Legislative Uncertainty

### 2016-05-10 presentation.tex
add slide on simultaneous model; small fixes throughout presentation

\pause
Leg $i$ votes for $s$ if $v(i) = \alpha -\beta i + \ta_i + a_i - b_i \leq 0$
	\begin{itemize}[<+->]
		\item Probability $i$ votes for $s$ is
			\[ 
				\Pr\left[\alpha -\beta i + \ta_i + a_i - b_i \leq 0 \right]
			\]
			\[
				= \Pr\left[\ta_i \leq \beta i - \alpha - a_i + b_i \right]
			\]
		\item Assuming $\ta_i \text{ i.i.d.} \sim \text{Logistic} \ (0,1): \ = \frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$ 
	\end{itemize}

@@

\begin{frame}{Vote Buyer B's Full Program}
\pause
\begin{equation}
    \left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1 - \lambda_X}{W_B}
		\label{eq:focB}
\end{equation}
\begin{equation}
    \left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1 - \lambda_Y}{W_B}
\end{equation}
\begin{equation}
    \left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2} = \frac{1 - \lambda_Z}{W_B}
\end{equation}
\[
  b\left(0\right) \geq0 \hskip.2in b\left(-.5\right) \geq0 \hskip.2in b\left(.5\right) \geq0 
\]
\[
  \lambda_X \geq0 \hskip.2in \lambda_Y \geq0 \hskip.2in \lambda_Z \geq0 
\]
\[
  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(-.5\right) = 0 \hskip.2in \lambda_Z \cdot b\left(.5\right) = 0 
\]

@@

\begin{frame}{Vote Buyer A}
\pause
Vote Buyer A is just like Vote Buyer B \textit{except}
\pause
\begin{itemize}[<+->]
	\item She gets to move first (in sequential model)
	\item She wants $x$ to win instead of $s$
	\item Willingness-to-pay parameter $W_A$
\end{itemize}
\end{frame}

@@

\pause
Let $X$ and $Y$ and $Z$ be the gross positions of each of the three legislators. Then the FOCs are
\pause
	\begin{equation}
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
	\end{equation}
	\begin{equation}
		\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
	\end{equation}

@@

\begin{frame}{Three Non-Negative Bribes}
Similar intuition for the case where all three legislators are bribed
\pause
\vskip.4in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Three Non-Negative Bribes}
    When Vote Buyer $B$ pays bribes to all three legislators, the bribes are such that the legislators' ideal points gross of bribes are equalized.
\end{beamerboxesrounded}
\end{frame}

@@

\subsection{Simultaneous Model}
\begin{frame}{Some Possibilities...}
What I know...
\begin{itemize}
	\item FOCs look the same as for one vote buyer, e.g.
		\begin{equation*}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
		\end{equation*}
			\begin{itemize}
				\item Two roots, only larger one satisfies SOC
			\end{itemize}
\end{itemize}

>>>>

\pause
Leg $i$ votes for $s$ if $v(i) = \alpha -\beta i + \ta_i + a_i - b_i \leq 0$
\pause
	\begin{itemize}[<+->]
		\item Probability $i$ votes for $s$ is
		\pause
			\[ 
				\Pr\left[\alpha -\beta i + \ta_i + a_i - b_i \leq 0 \right]
			\]
		\pause
			\[
				= \Pr\left[\ta_i \leq \beta i - \alpha - a_i + b_i \right]
			\]
		\pause
		\item Assuming $\ta_i \text{ i.i.d.} \sim \text{Logistic} \ (0,1): \ = \frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$ 
	\end{itemize}
\end{frame}

@@

\begin{frame}{Vote Buyer B's Full Program}
\pause
Let $X$, $Y$, $Z$ be the gross positions of the legislators
\pause
\begin{equation}
    \left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1 - \lambda_X}{W_B}
		\label{eq:focB}
\end{equation}
\begin{equation}
    \left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1 - \lambda_Y}{W_B}
\end{equation}
\begin{equation}
    \left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2} = \frac{1 - \lambda_Z}{W_B}
\end{equation}
\[
  b\left(0\right) \geq0 \hskip.2in b\left(-.5\right) \geq0 \hskip.2in b\left(.5\right) \geq0 
\]
\[
  \lambda_X \geq0 \hskip.2in \lambda_Y \geq0 \hskip.2in \lambda_Z \geq0 
\]
\[
  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(-.5\right) = 0 \hskip.2in \lambda_Z \cdot b\left(.5\right) = 0 
\]

@@

\begin{frame}{Vote Buyer A}
\pause
Vote Buyer A is just like Vote Buyer B \textit{except}
\pause
\begin{itemize}[<+->]
	\item She gets to move first (in sequential model)
	\item Willingness-to-pay parameter $W_A$
	\item She wants $x$ to win instead of $s$
		\begin{itemize}
			\item Leg $i$ votes for $x$ w/probability
				\[
					1 - \frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}} = \frac{e^{-\left(\beta i - \alpha - a_i + b_i \right)}}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}
				\]
		\end{itemize}

\end{itemize}
\end{frame}

@@

\pause
The FOCs are
\pause
	\begin{equation}
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
	\end{equation}
	\begin{equation}
		\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
	\end{equation}

@@

\begin{frame}{Three Non-Negative Bribes}
Similar intuition for the case where all three legislators are bribed:
\pause
\vskip.4in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Three Non-Negative Bribes}
    When Vote Buyer $B$ pays bribes to all three legislators, the bribes are such that the legislators' ideal points gross of bribes are equalized.
\end{beamerboxesrounded}
\end{frame}

@@

\subsection{Simultaneous Model}
\begin{frame}{What I know...}
\pause
FOCs look the same for Vote Buyer B, e.g.
\pause
	\[
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
	\]
	\vskip-.15in
	\pause
		\begin{itemize}
			\item Either one root at zero, or
			\pause
			\item Two roots and only larger one (at $X_B>0$?) satisfies SOC
		\end{itemize}

\vskip.1in
\pause
For Vote Buyer A,
\pause
	\[
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{1}{\left(1+e^{-X}\right)^2}= \frac{1}{W_A}
	\]
	\vskip-.15in
	\pause
		\begin{itemize}
			\item One root: zero or $X_B<0$
		\end{itemize}
